%%%%%%%%%%%%%%%%% PREAMBLE %%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Change the font size of your document - 10pt, 12.1pt, etc.
\documentclass[letterpaper,12pt,oneside]{article}
\usepackage[utf8]{inputenc}
\usepackage{setspace,marvosym,longtable}
%\usepackage{garamondlibre}
\usepackage{CormorantGaramond}
%\usepackage{ebgaramond}
\usepackage{hyperref,bibentry}

\usepackage{graphicx}
\graphicspath{ {images/}} %upload your signature to this file
%Change the margins to fit your CV/resume content
\usepackage[left=0.5in, right=0.5in, bottom=1.25in, top=1.25in]{geometry}

%Skype information - include your Skype name for a link to add you on Skype
\newcommand*{\Skype}{\href{skype:john.smith?add}{john.smith}} 
\newcommand{\Absender}[1][\normalsize]{\Skype} 

%Changes the page numbers - {arabic}=arabic numerals, {gobble}=no page numbers, {roman}=Roman numerals
\pagenumbering{gobble}

%%%%%%%%%%%%%%%%% END OF PREAMBLE %%%%%%%%%%%%%%%%%%%%%

\begin{document}
\nobibliography{references}
\bibliographystyle{unsrt}

%%%%%%%%%%%%%%%%% NAME OF APPLICANT %%%%%%%%%%%%%%%%%%%

\noindent  \LARGE{\textbf{Christopher A. Schroeder}} \\
\vspace{-2ex} 
\hrule 
\normalsize

%%%%%%%%%%%%%%%%% CONTACT INFORMATION %%%%%%%%%%%%%%%%%

\begin{center}
\begin{tabular}{l l}
 Binghamton University    & \hspace{1in} 
 \Letter \, cschroe2@binghamton.edu \\
 Department of Mathematics and Statistics & \hspace{1in}  \Mundus \url{https://sites.google.com/view/cschroeder}  \\
 %https://sites.google.com/view/cschroeder  \\
 Binghamton, NY 13902 & \hspace{1in} Citizenship: USA %\hspace{1in}   \\
 %xxx & %\hspace{1in} Birthdate: 22.10.1987 \\
\end{tabular}
\end{center}

\vspace{1em}

%%%%%%%%%%%%%%%%% MAIN BODY %%%%%%%%%%%%%%%%%%%%%%%%%%%
% The main body is contained in a tabular environment. To move sections onto the next page, simply end the tabular environment and begin a new tabular environment.

%\noindent \begin{tabular}{@{} l l}

%% Education
\noindent \begin{longtable}{p{0.15\linewidth}p{0.7\linewidth}p{0.15\linewidth}}
 \large{Education}    & \textbf{Binghamton University}, Binghamton, NY & 2021-- \\
     & Ph.D. in Mathematics (\emph{Expected 5/2026}) %GPA: 4.0 
     & \\
     & Research interests: representation theory, finite group theory & \\
     & Dissertation: \emph{Invariants of finite groups} &\\
     & Advisor: Hung Tong-Viet & \\
     & \\
    & \textbf{University of Maryland}, College Park, MD & 2011--2016 \\
     & Ph.D. in Physics & \\ %GPA: 4.0
     & Research interests: quantum effects in biology, open quantum systems & \\
     & Dissertation: \emph{Exploiting collective effects to direct light absorption in} \\& \quad \emph{natural and artificial light-harvesters} & \\
     & Advisors: Luis Orozco and Martin Plenio & \\
     & \\
     & \textbf{University of Oklahoma}, Norman, OK & 2006--2011 \\
     & B.Sc. in Mathematics, B.Sc. in Physics, B.A. in German. & \\ %GPA: 4.0 & \\
    & &\\
  \large{Academic}   & \textbf{Binghamton University}, Binghamton, NY  & 2021--2025  \\
  \large{Positions}  & Mathematics instructor  & \\
     & & \\

     & \textbf{Bethany College}, Lindsborg, KS & 2019 -- 2021  \\
     & Assistant Professor of Mathematics & \\
     & & \\
     
     &\textbf{Northeastern State University}, Tahlequah, OK & 2017--2018\\
     & Adjunct Professor of Mathematics & \\
     & & \\
     & \textbf{Bard High School Early College}, Baltimore, MD & 2016--2017 \\
     & Mathematics Faculty & \\
     & &\\
     & \textbf{Institute for Theoretical Physics}, Ulm, Germany & 2013--2015 \\
     & Researcher (studentische Hilfskraft) & \\
    &&\\

%%% Fellowships
\large{Fellowships} & Binghamton Graduate Student Award for Excellence in Research & 2026 \\
  \large{and} & Binghamton Graduate Student Award for Excellence in Teaching & 2026 \\
\large{Awards} & Binghamton Dissertation Year Fellowship & 2026 \\
  & NSF Graduate Research Fellowship & 2013--2016 \\
  & University of Maryland Department of Physics Excellence in Teaching Award & 2012 \\
  & DAAD RISE Scholarship, Stuttgart Germany & 2009 \\
     & University of Oklahoma prize for outstanding physics student & 2007-2010 
\end{longtable}

%% Publications
\noindent \begin{longtable}[l]{p{0.15\linewidth}p{0.7\linewidth}}
\large{Publications} & \textbf{C. Schroeder} and H.P.~Tong-Viet. On the invariants of finite groups arising in a \\ 
\large{and Preprints} & topological quantum field theory. {\tt arXiv:2510.14971 [math.GR]} (2025). \\
&\\
 & \textbf{C.~Schroeder} and H.~P. Tong-Viet, Finite groups all of whose maximal subgroups have almost odd index, J. Pure Appl. Algebra {\bf 229} (2025), no.~11, Paper No. 108108. \\
&\\

& \textbf{C. Schroeder}. Finite groups with many $p$-regular conjugacy classes. J. Algebra 641 \\
& (2024), 716--734. \\
&\\

%&\textbf{C. Schroeder.} Projective characters of almost odd degree. \emph{In preparation.}\\
%&\\

%&\textbf{C. Schroeder.} Refining group invariants with class functions. \emph{In preparation.}\\
%&\\

& B.~Huppert and \textbf{translated by C.~Schroeder}. \emph{Finite Groups I}. Die Grundlehren der mathematischen Wissenschaften, Volume 364, Springer-Verlag, Berlin (2025).\\
&\\
 
& F. Caycedo-Soler, \textbf{C. Schroeder}, C. Autenrieth, A. Pick, R. Ghosh, S.F. Huelga,and M. Plenio. Quantum redirection of antenna absorption to photosynthetic reaction centers. \emph{The Journal of Physical Chemistry Letters}, 8 (2017). \\
& \\
     
& \textbf{C. Schroeder}, F. Caycedo-Soler, S.F. Huelga, and M. Plenio. Optical signatures of quantum delocalization over extended domains in photosynthetic membranes. \emph{The Journal of Physical Chemistry A}, 119 (2015). \\
& \\

& A. Cimmarusti, \textbf{C. Schroeder}, B. Patterson, L. Orozco, P. Barberis-Blostein, and H. Carmichael. Control of conditional quantum beats in cavity QED: amplitude decoherence and phaseshifts. \emph{New Journal of Physics}, 15 (2013). \\
& \\

& A. Cimmarusti, B. Patterson, \textbf{C. Schroeder}, L. Orozco, P. Barberis-Blostein, and H. Carmichael. Feed-back in a cavity QED system for control of quantum beats. \emph{EPJ Web of Conferences}, 57 (2013). \\
& \\

& \textbf{C. Schroeder} and  G.S. Agarwal. Optimized pulse sequences for suppressing unwanted transitions in quantum systems. \emph{Phys. Rev. A}, 83 (2011). 
\end{longtable}


%\noindent \begin{tabular}{@{} l l}
\noindent \begin{longtable}{p{0.15\linewidth}p{0.7\linewidth}p{0.15\linewidth}}

\large{Talks} 
& AMS Central Meeting. St. Louis, MO. \emph{invited talk.} & 2025 \\
& Postgraduate Group Theory Conference. Bristol, UK. \emph{contributed talk.} & 2025 \\
& AMS Eastern Meeting. Hartford, CT. \emph{invited talk.} & 2025 \\
& AMS Western Meeting. San Francisco, CA. \emph{invited talk.} & 2024\\
& Binghamton Algebra Seminar. Binghamton, NY; \emph{7 contributed talks} & 2021-2025 \\
& Zassenhaus Groups and Friends Conference. Online; \emph{2 contributed talks} & 2021-2025 \\
 & BUGCAT. Binghamton, NY; \emph{3 contributed talks} & 2021-2025\\
 & Algebra 2022 and Beyond. Bloomington, IN. \emph{contributed talk} & 2022 \\ 
 & Quantum Mechanics and Biology Workshop. Traunkirchen, Austria; \emph{lecturer} & 2015\\
     & Quantum Effects in Biological Systems. Florence, Italy; \emph{poster} & 2015 \\
     
     & DPG Spring Meeting. Heidelberg, Germany; \emph{contributed talk} & 2015\\
     
     & Quantum Effects in Biological Systems. Singapore; \emph{poster} & 2014 \\
     
     & Australian Institute of Physics Congress. Canberra, Australia; \emph{contributed talk} & 2014 \\
     
     & Gordon Research Conference (GRC) on Photosynthesis. West Dover, VT; \emph{poster} & 2014\\
     
    & Quantum Effects in Biological Systems. Vienna, Austria; \emph{poster} & 2013 \\
    
    & American Physical Society, AMO division; \emph{poster} & 2012\\
    
    & Oklahoma EPSCOR Undergraduate Research Day at the Capitol; \emph{talk} & 2010 \\ \\


%%% Advising
 \large{Advising}    & Master's thesis in quantum optics, Ulm, Germany & 2014 \\
   & Bachelor's thesis in biophysics, Ulm, Germany & 2013 \\
     & & \\

%%% Service
 \large{Reviewing}    & I have refereed papers for the following mathematical journals: &\\
 & $\cdot$ Journal of Group Theory & \\
 & $\cdot$ International Journal of Group Theory & \\
     & & \\

%%% Teaching
\large{Teaching} & Instructor of record at Binghamton University & 2021--2025 \\
    & Math 148 - Elementary Statistics for Biologists (Fall `21, Spring `22) \\
    & Math 224 - Differential Calculus (Fall `22, Summer `23) \\
    & Math 225 - Integral Calculus (Fall `22, Spring `23, Fall `24) \\
    & Math 226 - Integration Techniques (Spring `23, Fall `23, Spring `24, Fall `24, Spring~`25, Fall `25) \\
    & Math 227 - Sequences and Series (Fall `23, Spring `24, Spring `25, Fall `25)   \\
    &&\\
    &Assistant Professor of Mathematics at Bethany College & 2019--2021 \\
    & College Algebra, Math for the People\\
    &&\\
    &Adjunct Professor of Mathematics, NSU OK & 2017--2018 \\
    & College Algebra, Calculus I, Discrete Math \\
    &&\\
    &Math Faculty at Bard High School Early College & 2016--2017 \\
    & Geometry, Statistics \\&&\\
    
    \large{Programming}   & Fortran, GAP, Gromacs, Latex, Matlab, Mathematica, Python \\ &&\\

    \large{Languages}  & English, German

\end{longtable}

\end{document}

%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%%%%%%%%%
% The reference section has links to your references' websites and email addresses.

%\noindent \begin{tabular}{@{} l l l}
% \Large{References} & \href{http://www.professorone.com}{Professor One} & \href{http://www.professortwo.com}{Professor Two} \\
% & Department Name &  Department Name  \\
% & University Name &  University Name \\
% & \small{\href{mailto:prof1@email.com}{prof1@email.com},+1\,(123)\,456-7899} & \small{\href{mailto:prof2@email.com}{prof2@email.com},+1\,(987)\,654-3210} \\
%&& \\
% & \href{http://www.professorthree.com}{Professor Three} & \href{http://www.professorfour.com}{Professor Four}  \\
% & Department Name &  Department Name \\
% & University Name &  University Name \\
% & \small{\href{mailto:prof3@email.com}{prof3@email.com},+1\,(123)\,789-1011} & \small{\href{mailto:prof4@email.com}{prof4@email.com},+1\,(789)\,456-9879} \\
%\end{tabular}